---
title: "Vignette Lab4"
author: "Erika Anderskar & Georgia Mushe"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Lab4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r}
devtools::use_package("Lab4")
devtools::use_package("ggplot2")
linreg$print()
```
The Lab4 package consists of one function, linreg. Linreg is a function, of class RC, to calculate a linear regression model. The function needs two arguments to work, formula and data. The formula has to be written as a formula, it starts with the response variable followed by "~" and ends with all the explanatory variables. The explanatory variables are seperated by "+".

Ex, Y ~ X1 + X2 + X3

The linreg function contains six subfunctions which prints different results. The following functions are implemented:

| Function  | Description                                                               |
|-----------|---------------------------------------------------------------------------|
| print()   | prints a formula and the coefficients                                     |
| plot()    | plots 'Residuals vs Fitted' and 'Scale-Location' `ggplot2`                |
| resid()   | returns a vector of residuals $\hat{e}$                                   |
| pred()    | returns a vector of predicted values $\hat{y}$                            |
| coef()    | returns the coefficients                                                  |
| summary() | returns the coefficients, standard error, t-values and p-values           |



## Call the functions

In the following the different functions are described and the corresponding outputs are shown.

The object name is linreg and the functions will therefore be called by`linreg$functionname`.

### print()

The `print()` prints the formula and the coefficients of the estimated linear regression model.

```{r}
linreg$print()
```
### plot()

The `plot()` function uses `ggplot2` to plot residuals vs. fitted values and the scale location.

```{r, results = 'hide', message = FALSE, fig.width = 5}
linreg$plot()
```


### resid()
The `resid()` function returns a vector of the residuals of the estmated linear regression model.
```{r}
linreg$resid()

```

### pred()
The `pred()` function returns a vector of the predicted values of the estimated linear regression model.
```{r}
linreg$pred()
```

### coef()
The `coef()` function returns the coefficients of the estimated linear regression model.
```{r}
linreg$coef()
```

### summary()
The `summary()` function returns the coefficients, standard errors, t-values and p-values of the estimated linear regression model.
```{r}
linreg$summary()
```

